### 2014-09-29 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG_Co: update figures and minor update to report

@@

\section{Geometry}
\label{geom}
The structure involved in this fire incident was a one story, single-family structure with a basement. Due to the surrounding topography (the ground slopes from the front to rear of the structure), the basement on the rear side of the structure was above grade. The structure was wood-framed platform-framed with a gable roof. \footnote{Platform-framed construction means that floor joists are completely covered with a sub-floor. This forms a platform for which walls are built from.} The structure had a first floor footprint of 9.14~m (30~ft) by 7.77~m (25.5~ft) with the basement being slightly smaller, 9.14~m (30~ft) by 7.16~m (23.5~ft), as show in Fig.~\ref{fig:simp_geom}. This results in a first floor area of 71~m$^2$ (764~ft$^2$) and a basement floor area of 65~m$^2$ (700~ft$^2$). The interior walls and ceiling were constructed from nominal lumber covered by 12.7~mm (0.5~in) gypsum board~\cite{PGCounty2013}. There is a single flight of stairs in the center of the structure which connected the first floor to the basement. Access to the structure could be made on the front side of the first floor and the rear side of the basement.

@@

\begin{figure}[!ht]
\centering
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   \scalebox{1.0}{\includegraphics[width=\textwidth]{../Figures/pg_county_meshfront}} \\
   \scalebox{1.0}{\includegraphics[width=\textwidth]{../Figures/pg_county_meshrear}} 
\end{tabular*}
\caption{Front (left) and rear (right) of the structure with 10~cm computational mesh.}
\label{fig:geom_grid}
\end{figure}

>>>>

% PDF metadata
\hypersetup{
  pdftitle={Simulation of a Wind Driven Basement Fire - Riverdale Heights, MD},
  pdfauthor={Weinschenk, Craig G., Overholt, Kristopher J., and Madrzykowski, Daniel},
  pdfsubject={Insert abstract here.},
  pdfkeywords={insert; keywords; here}
}

@@

\section{Geometry}
\label{geom}
The structure involved in this fire incident was a one story, single-family structure with a basement. Due to the surrounding topography (the ground slopes from the front to rear of the structure), the basement on the rear side of the structure was above grade. The structure was wood-framed platform-framed with a gable roof. \footnote{Platform-framed construction means that floor joists are completely covered with a sub-floor. This forms a platform for which walls are built from.} The structure had a first floor footprint of 9.14~m (30~ft) by 7.77~m (25.5~ft) with the basement being slightly smaller, 9.14~m (30~ft) by 7.16~m (23.5~ft), as show in Fig.~\ref{fig:simp_geom}. This results in a first floor area of 71~m$^2$ (764~ft$^2$) and a basement floor area of 65~m$^2$ (700~ft$^2$). The interior walls and ceiling were constructed from nominal lumber covered by 12.7~mm (0.5~in) gypsum board~\cite{PGCounty2013}. There was a single flight of stairs in the center of the structure which connected the first floor to the basement. Access to the structure could be made on the front side of the first floor and the rear side of the basement.

@@

\begin{figure}[!ht]
\centering
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   \scalebox{1.0}{\includegraphics[width=\textwidth]{../Figures/pg_county_meshfront}} \\
   \scalebox{1.0}{\includegraphics[width=\textwidth]{../Figures/pg_county_meshrear}} 
\end{tabular*}
\caption{Front (top) and rear (bottom) of the structure with 10~cm computational mesh surrounding the structure and 20~cm mesh to the left and right of the structure.}
\label{fig:geom_grid}
\end{figure}
